### 2019-01-10 thesis_report/methods.tex
Updated thesis

\chapter{Methods}

\section{Sparse eigendecomposition of kwant system}
	\subsection{Wrapped system}
	\subsection{Finite system}

\section{Scattering matrix formalism}

>>>>

\chapter{Methods}
% UNCOMMENT TO USE LaTeXing autocomplete for refereces
% \bibliography{report}

\comment{We propose a method to verify that elimination of long trajectories is responsible for the increased topological gap in a zigzag system.}
\section{Quasiclassical estimation of the topological gap}
	\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
	In order to establish that the elimination of long trajectories is the driving mechanism behind the order of magnitude gap improvement, we use an analytical approach.
	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag.
	The spectrum of the zigzag segment we define as the spectrum of an infinite ribbon SNS junction with tilted-magnetic field. 
	The finite length of the segment is modeled by not including momenta corresponding to long trajectories when taking the minimum over the spectrum.

	\comment{The spectrum is derived using a scattering matrix, and we consider multiple ways to eliminate long trajectory momenta.}

	Estimating the gap is a two-step process: derivation of the Andreev spectrum, and taking the minimum energy over a particular set of allowed momenta.
	The first is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
	The second step is mostly trivial, but the difficulty lies with identifying the set of allowed  momenta to take the minimum over.

	\subsection{Analytical estimate of Andreev spectrum for a straight junction}

		\comment{We use a short junction approximation and neglect transverse SO.}
		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
		The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.

		In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:

		\begin{equation}
		\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
		\end{equation}

		We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as

		\begin{equation}
		\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
		\end{equation}

		with
		\begin{equation}
		\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
		\end{equation}

		Where $\lambda_i$ are the eigenvalues of $A$.
		Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
		Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
		Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

		\subsubsection{Derivation of the scattering matrix}
			We consider the scattering problem defined by Fig. \ref{fig:scattering}, the corresponding system of equations given in Eq. \eqref{eq:scattering_matrix_problem}, and
			continuity and flux conservation(continuity of first derivative) at the normal-superconductor interfaces.
			The Hamiltonians of the respective regions are given by Eqs. \eqref{eq:ham_smat_normal,eq:ham_smat_superconducting}.
			The Hamiltonian of the superconducting region does not include the superconducting term because we implement Andreev reflection seperately: this way we halve the dimensionality of the problem.

			\begin{equation}
			\begin{bmatrix} 
			b_{1,L}\\
			b_{2,L}\\
			b_{1,R}\\
			b_{2,R}
			\end{bmatrix} 
			= S_\text{sns} \cdot 
			\begin{bmatrix} 
			a_{1,L}\\
			a_{2,L}\\
			a_{1,R}\\
			a_{2,R}
			\end{bmatrix}
			\label{eq:scattering_matrix_problem}
			\end{equation}

			\begin{align}
			H_\text{N} &= \left[ \frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_n\right]\sigi +
						 \alpha \kx \sigy +
						 E_z \left[ \cos(\theta) \sigx + \sin(\theta) \sigy \right]
			\label{eq:ham_smat_normal} 
			\\
			H_\text{S} &= \left[\frac{\hbar^2}{2 \meff} \left(\kx^2 + \ky^2\right) -\mu_s\right]\sigi
			\label{eq:ham_smat_superconducting}
			\end{align}

			\begin{figure}[!htb]
			\includegraphics[width=0.95\columnwidth]{images/scattering}
			\caption{Basis for scattering matrix. `S' region corresponds to the superconductor Hamiltonian without the superconducting term.}
			\label{fig:scattering}
			\end{figure}

			The resulting scattering matrix:

			\begin{align}
			\label{eq:smatrix}
		    S &= \left(
		    \begin{array}{rr}
		    r_{ll}&t_{rl}\\
		    t_{lr}&r_{rr}\\
		    \end{array}
		    \right) =
		    \left(
		    \begin{array}{rr}
		    \beta_+ & e^{-i q W} \beta_-\\
		    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
		    \end{array}
		    \right)
		    \\
		    \beta_\pm &= \left(
		    \begin{array}{rr}
		    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
		    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
		    \end{array}
		    \right)\\
		    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
			\end{align}

			\begin{align}
			    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
			    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
			    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
			\end{align}

			\begin{footnotesize}
			\begin{align}
			    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
			    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
			    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
			\label{eq:momenta_short_junction}
			\end{align}
			\end{footnotesize}

		\subsubsection{Resulting spectrum}
			In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:

			\begin{equation}
			\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
			\end{equation}

			We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as

			\begin{equation}
			\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
			\end{equation}

			with
			\begin{equation}
			\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
			\end{equation}

			Where $\lambda_i$ are the eigenvalues of $A$.
			Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
			Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
			Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

	\subsection{Eliminating long trajectories}
		\comment{We devise two different ways to define the cutoff of momentum.}

		\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.75\columnwidth]{images/zigzag.pdf}
		\caption{Setups. Figure of a straight and zigzag system, including trajectories.
		\label{fig:setup}}
		\end{figure}

		\subsubsection{Momentum cutoff}
			We take the longest trajectory possible in a zigzag segment
		\subsubsection{Angular cutoff}

### 2019-01-10 thesis_report/results.tex
Updated thesis

\documentclass[english, twocolumn, 10pt, aps, superscriptaddress, floatfix, prb, citeautoscript]{revtex4-1}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{verbatim}
\usepackage{units}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{wasysym}
\usepackage{layouts}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{xcolor}
\usepackage[colorlinks, citecolor={blue!50!black}, urlcolor={blue!50!black}, linkcolor={red!50!black}]{hyperref}
\usepackage{bookmark}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage{babel}
\hypersetup{pdfauthor={Quantum Tinkerer},pdftitle={Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.}}

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\DeclareMathOperator{\e}{e}
\DeclareMathOperator{\de}{d\!}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Pf}{Pf}
\DeclareMathOperator{\Det}{Det}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\re}{Re}
\newcommand{\kx}{k_x}
\newcommand{\ky}{k_y}
\newcommand{\meff}{m_\text{eff}}

\renewcommand{\comment}[2]{#2}
% Uncomment the following line for paragraph descriptions to appear in the file.
\renewcommand{\comment}{\paragraph}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

\newcommand{\ev}[1]{\langle#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bracket}[2]{\langle#1|#2\rangle}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}

\begin{document}

\title{Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.}

\author{Quantum Tinkerer}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{quantumtinkerer@tudelft.nl}

\date{\today}
\begin{abstract}
We are solving a problem of soft gap in high density SNS Majorana junctions \cite{pientka2017topological}.
We do this by introducing a zigzag geometry.
This works because the maximum trajectory length is cut-off due to the geometry and therefore the minimal energy gap is given by a simple formula, which we also verify using numerics.
In addition to having a large minimum energy gap, the absence of long length trajectories means that the localization length is very short as well.
\end{abstract}

\maketitle

%%██████████████████████████████████████████████████████████████████████████
%%██ Introduction
%%██████████████████████████████████████████████████████████████████████████
\section{Introduction}
Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.

\comment{Majoranas are mostly made in hybrid NS structures.}
The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
\comment{We consider a two-dimensional system with zigzag.}
We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
Both parts have a kinetic term and chemical potential $\mu$. 
For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
Later in this manuscript we show that the exact details of the shape are not important and consider different zigzag geometries also parametrized by $z_x, \; z_y, \; W$.

\comment{The symmetry class of the system is D.}
The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral symmetry $\mathcal{C}$ resulting from the mirror symmetric junction.

\begin{small}
\begin{align}
    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
        E_\text{z} \sigma_x+
        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
        \Delta \tau_y
\end{align}
\label{eq:hamiltonian}
\end{small}

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/zigzag.pdf}
\caption{Setups. Figure of a straight and zigzag system, including trajectories.
\label{fig:setup}}
\end{figure}

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the bandstuctures
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the bandstuctures.}

\comment{We discretize the model described in section II and simulate it with Kwant.}
We discretize our continuum Hamiltonian \eqref{eq:hamiltonian} and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell in order to make the structure periodic.
To speed up these expensive simualtions we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add citation

\comment{We calculate the bandstructure for varying amount of zigzag.}
In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
Because the discretized zigzag system is modeled using a super cell, we can only plot a folded bandstructure.
For comparisons sake, we take the same cell size for the ribbon structure such that the bandstructure is folded in the same way.

\comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased by more than an order of magnitude.
This happens because in a straight system, long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
The smallest gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size is increased. 
Besides this, the velocity of the modes is greatly reduced, which has a positive effect on the Majorana coherence length, as described later in section XXX. % TODO: add ref

\comment{The introduction of an SN interface at many angles also increases performance.}
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a perpendicular surface.
This means that for transversal modes the transparency of the NS interface will increase.

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the topological phase diagram
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the topological phase diagram.}

\comment{We calculate the topological phase diagram using the gap size.}
We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Analytical estimate
%%██████████████████████████████████████████████████████████████████████████
\section{Analytical estimate of the band gap}

\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
We establish that the cutoff of long trajectories is the driving mechanism behind the order of magnitude gap improvement using an analytical approach.
We derive the Andreev spectrum for a single (diagonal) segment of the zigzag, and define the gap of the system as the minimum of the spectrum occurring before the cutoff corresponding to the particular geometry.
The system under consideration is thus a ribbon SNS junction with tilted magnetic field.

\comment{The definition of the cutoff... }

\comment{We use a short junction approximation and neglect transverse SO.}
We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.

\begin{align}
\label{eq:smatrix}
    S &= \left(
    \begin{array}{rr}
    r_{ll}&t_{rl}\\
    t_{lr}&r_{rr}\\
    \end{array}
    \right) =
    \left(
    \begin{array}{rr}
    \beta_+ & e^{-i q W} \beta_-\\
    e^{-i q W} \beta_- & e^{-2 i q W} \beta_+\\
    \end{array}
    \right)
    \\
    \beta_\pm &= \left(
    \begin{array}{rr}
    e^{i \nu_{\arg}}\left(\omega^\pm_1 - \omega^\pm_2\right) & (\omega^\pm _1 + \omega^\pm _2)\\
    -(\omega^\pm _1 + \omega^\pm _2) & e^{-i \nu _{\arg }} \left(\omega^\pm _2 - \omega^\pm _1\right)\\
    \end{array}
    \right)\\
    \omega^\pm_j &= \frac{1}{4} \left(\gamma _{j} \pm \delta _{j}\right)
\end{align}

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}

\begin{footnotesize}
\begin{align}
    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
\label{eq:momenta_short_junction}
\end{align}
\end{footnotesize}

In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\onlinecite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:

\begin{equation}
\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
\end{equation}

We rewrite this as a characteristic polynomial problem $\det\left[A-\lambda I\right]=0$, as

\begin{equation}
\det\left[r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)-\frac{-1}{\alpha^{2}\left(E\right)}I\right]=0
\end{equation}

with
\begin{equation}
\lambda=-\frac{1}{\alpha^{2}\left(E\right)},\;A=r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right).
\end{equation}

Where $\lambda_i$ are the eigenvalues of $A$.
Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ yields $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}
We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

%%██████████████████████████████████████████████████████████████████████████
%%██ Localization lengths and shape effect
%%██████████████████████████████████████████████████████████████████████████
\section{Localization lengths and shape effects}

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Discussion and Conclusions
%%██████████████████████████████████████████████████████████████████████████
\section{Discussion and Conclusions}

\comment{The zigzag geometry is a useful tool in hardening the gap and decreasing majorana length, now experimental verification necessary}
The introduction of a zigzag geometry increases the topological gap by over an order of magnitude, as well as offering a substantial reduction of the Majorana length.
Additionally, the breaking of BDI symmetry into D symmetry results in a cleaner topological region.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry; zigzag devices have already been created.
Slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake like and offset sinosoid modulation of the semicondctor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majorana's would be an interesting continuation.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
We omit several physical effects, such as: disorder, electrostatics, the orbital effect, etc..
Further study, as well as experimental verification, are required to see whether the conclusions of this model are valid for the real case.

\comment{Acknowledgments}

We are grateful to "people" for useful discussions.
This work was supported by the Netherlands Organization for Scientific Research (NWO/OCW), as part of the Frontiers of Nanoscience program, the Foundation for Fundamental Research on Matter (FOM), and an ERC Starting Grant STATOPINS 638760.

\bibliographystyle{apsrev4-1}
\bibliography{snakemajoranas}
\end{document}

>>>>

\chapter{Results \& Discussion}

	\comment{We see that the introduction of a zigzag leads to a reduction of the gap}
	\section{Gap/bandstructure as a function of zigzagginess}
		\comment{We discretize the model described in section II and simulate it with Kwant.}
		We implement a tightbinding version of the model described in the Methods section (a two dimensional SNS junction with a Rashba BdG Hamiltonian) using Kwant.

@@

		\comment{We calculate the bandstructure for varying amount of zigzag.}
		In figure~\ref{fig:bandstuctures}, the bandstructure for zigzag systems with varying amplitude is displayed.
		As the zigzag introduces super cell, we see a folded bandstructure.
		For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.

		\comment{The bandstructures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
		The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
		This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
		Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
		This has an effect on the Majorana coherence length, as described later on in the manuscript.

		\comment{The introduction of an SN interface at many angles also increases performance.}
		Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to. The transparency of the SN interface is thus improved for transversal modes.

	\comment{Introduction of a zigzag leads to localization of the Majorana's}
	\section{Majorana decay length}
		\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}

@@

	\comment{Zigzag Majorana's have a cleaner phase diagram due to the reduction in symmetry class}
	\section{Phase diagram}
		\comment{We calculate the topological phase diagram using the gap size.}
		We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
		Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

	\comment{We use our analytical bandstructure to }
	\section{Analytical estimate}

### 2019-01-10 thesis_report/theory.tex
Updated thesis

% Momentum operators
\newcommand{\kx}{k_x}
\newcommand{\ky}{k_y}

% Pauli matrices
\newcommand{\sigx}{\sigma_x}
\newcommand{\sigy}{\sigma_y}
\newcommand{\sigz}{\sigma_z}
\newcommand{\sigi}{\sigma_0}
\newcommand{\taux}{\tau_x}
\newcommand{\tauy}{\tau_y}
\newcommand{\tauz}{\tau_z}
\newcommand{\taui}{\tau_0}
\chapter{Theory}

\section{General Physics}
	\subsection{Boguliubov de Gennes Hamiltonian}

    \subsection{Spin-orbit coupling}
    Rashba spin orbit coupling:
    \begin{equation}
    	H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
    \end{equation}

    \subsection{Supercurrent}
	The current

	\subsection{Tight binding}

		\subsection{Topology in solid state physics}
		The Wikipedia definition of mathematical topology is as follows:

@@

\section{Majorana bound states}
	\subsection{General properties}
	\subsection{Decay length}
	\subsection{Topological gap}

\section{Two dimensional platform for Majoranas}
	\subsection{Phase diagram}
	\subsection{Current phase relationship}
	\subsection{Thouless energy}

>>>>

\chapter{Theory}

\section{General Physics}

    \subsection{Zeeman interaction}
    	The energy splitting of the two electron spin species due to magnetic field is called the Zeeman interaction.
    	It is modeled by:
    	\begin{equation}
    	H_\text{Z} = g \mu_B \vec{B} \cdot \vec{\sigma}
    	\end{equation}

    \subsection{Spin-orbit coupling}
	    An electron mvoing in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
	    The resulting interaction is known as spin orbit coupling.
	    Spin-orbit coupling can be approximated with adding a Rashba spin orbit coupling term in the Hamiltonian:
	    \begin{equation}
	    H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
	    \end{equation}

    \subsection{Superconductivity}
		Superconductivity manifests itself as the complete lack of electrical resistance of a material.
		It is the result of the pairing of electrons close to the Fermi-energy, condensing into so-called Cooper pairs.
		Because all electrons within a distance of the superconducting order parameter of the Fermi-energy are depleted in this way, charge transport only takes place via these quasiparticles.
		Scattering of these Cooper pairs is not allowed, resulting in perfect conduction.

		For the purpose of creating Majorana's, we are interested in two main aspects of superconductivity: the energy gap surrounding the Fermi energy (due to the depletion of states), and the electron-hole (/particle-hole) symmetry.
		We are thus not interested in the paired up electrons (Cooper pairs), and only wish to model the electronic (unpaired) modes.
		This can be achieved by modeling superconductivity with the Boguliubov de Gennes Hamiltonian:

		\begin{equation}
		\mathbf{H}_\text{BdG} = \begin{bmatrix} H & \Delta \\ \Delta^\dagger & H \end{bmatrix}
		\end{equation}

		The block matrix restricts the structure of the system in the electron-hole basis, and ensures particle-hole symmetry.
		For $\Delta \neq 0$ one indeed induces a identically sized gap in the spectrum.

		\subsubsection{Andreev scattering}
			At the interface between a normal and superconducting region, electrons with energies below the superconducting gap undergo Andreev scattering.
			The quasiclassical microscopic explanation for this is as follows.
			An electron in the normal region with energy below the superconducting gap, incident on the normal-superconductor (NS) interface, is retro-reflected as a hole.
			This phenomenon is known as Andreev scattering, and occurs due to the coupling of electrons in a superconductor.
			Although a single electron initially enters the superconductor, it draws another electron (with opposite momentum) into the superconductor: forming a Cooper pair.
			The drawn in electron leaves behind a hole in the normal conductor, which essentially backtracks the motion of the initial electron, hence the term retro-reflection.
			The same effect, but opposite in particle type, holds for a hole entering the superconductor.

		\subsubsection{Josephson junctions and supercurrent}

\section{Topology and Majorana bound states}
	\subsection{Topology in solid state physics}
	The Wikipedia definition of mathematical topology is as follows:

@@

	\subsection{General properties}
	\subsection{Decay length}
	\subsection{Topological gap}

\section{Two dimensional platform for Majoranas}
	\subsection{Phase diagram}
	\subsection{Current phase relationship}
	\subsection{Thouless energy}
	\subsection{Transparency at NS interface}
